\documentclass[a4paper,11pt]{article}

%\usepackage[latin1]{inputenc}
%\usepackage[italian]{babel}
%\usepackage{graphicx}
\usepackage{setspace} \usepackage{geometry} \usepackage{hyperref}
\geometry{a4paper,tmargin=30mm,bmargin=30mm,lmargin=30mm,rmargin=30mm}

\begin{document}
\pagestyle{empty}
\begin{center}
  \huge{Publications List}
\end{center}
\vspace{1cm}
{\bfseries Talks, Poster Sessions and Proceedings}
\begin{itemize}
\item Dubna Beam Energy Measurement Workshop, Joint Institute for
  Nuclear Research (JINR), Dubna, June 2006.
\item European Particle Accelerator Conference (EPAC 06), Edinburgh,
  Scotland, 26-30 June 2006.
\item Yerevan Beam Energy Measurement Workshop, Yerevan Physics
  Institute, Yerevan, October 2006.
\item DPG Fr\"uhjahrstagung, Heidelberg, 5-9 March 2007.
\item 2007 International Linear Collider Workshop (LCWS07 and ILC07),
  Hamburg, Germany, 30 May - 3 June 2007.
\item Zeuthen Beam Energy Measurement Workshop, Zeuthen, June 2007,
\item Particle Accelerator Conference PAC07, Albuquerque, New Mexico,
  25-29 June 2007.
\item DPG Fr\"uhjahrstagung, Freiburg, 3-7 March 2008.
\item Workshop on Polarization and Beam Energy Measurements at the
  ILC, Zeuthen, 9-11 April 2008.
\item ILC-ECFA Workshop, Warsaw, Poland, 9-12 June 2008.
\item EUDET Annual Meeting 2010, Hamburg, Germany, 29 September - 1 October 2010.
\item M. Viti, Forward Physics Results from ATLAS, Nuclear Physics B
  (Proc. Suppl.) $219-220$ (2011) $145-148$.
\item C. B. Wunderer et al. The PERCIVAL soft X-ray imager, presented at iWoRiD 2013, JINST 9 C03056, 2014
\item M. Viti et al. Spatial Resolution Studies for the PERCIVAL Sensor, iWoRiD 2014, Poster Session (Proceedings will be published in JINST) 
\item  C. B. Wunderer et al. The Percival Soft X-Ray Imager presented at iWoRiD 2014 (Proceedings will be published inh JINST)
\end{itemize}
{\bfseries Internal Notes}
\begin{itemize}
\item M. Viti and S. Kostromin, Magnetic measurements for magnets
  10D37, ILC-SLACESA TN-2008-1, 2008.
\item B. Allongue et al. Results from the ALFA test beam campaign in
  2009, ATL-COM-LUM-2010-031, CERN Geneva, October 2010.
\end{itemize}
{\bfseries Publications}
\begin{itemize} 
\item M. Viti, Precise and fast beam energy measurement at the
  International Linear Collider, DESY-THESIS-2010-007
\item N. Muchnoi, H. J. Schreiber and M. Viti, ILC beam energy
  measurement by means of laser Compton Backscattering,
  Nucl. Instrum. Meth., A607:340-366, 2009.
\item A. Lyapin et al. Results from a prototype chicane-based energy
  spectrometer for a linear collider JINST 6 (2011) P02002,
  arXiv:1011.0337
\item ATLAS authorship.
\end{itemize}
\end{document}
